Cartogram Mapping and Application to Cancer Data.

### 2019-05-08 review_article.Rmd
plan from today

---
title: "Cartogram Mapping and Application to Cancer Data."
output: html_document

toc: true
fig_caption: yes
number_sections: false
fontsize: 11pt
bibliography: reviewbib.bib
biblio-style: vancouver
link-citations: true
---

@@

## Spatial Visualisation of Disease

### Choropleth Map (current go to)

@@

### counts versus predictions

@@

Recognition of biases when utilising the geography to map people. Small areas contain more people, work towards representing regions of importance more clearly.

## Cartograms

## Temporal displays

## Alternatives

## Comparison of 
(only worth including if it is possible for us to implement)
Tabular form comparing and contrasting
- Relationship to geography

## Software
Commonly available tools to implement.

>>>>

---
title: "Cartogram Mapping and Application to Cancer Data."
output: html_document
fig_caption: yes
number_sections: false
fontsize: 11pt
bibliography: reviewbib.bib
biblio-style: vancouver
link-citations: true
---

@@

## Disease mapping

### Choropleth Map (Steff)

Cartographer lit, cancer atlas lit

@@

### Public face (Jessie)

what has been provided to the public, norms, common practices, all of Jessie's lit review

## Cartograms (Steff)

<!--
## Temporal displays
-->

### Centroid displays

## A critique choropleth and cartograms

(only worth including if it is possible for us to implement)
Tabular form comparing and contrasting
- Relationship to geography

## Acknowledgements

What software did we use, for eg

## References

<!--
## Software
Commonly available tools to implement.
-->

<!--
### counts versus predictions

@@

Recognition of biases when utilising the geography to map people. Small areas contain more people, work towards representing regions of importance more clearly.
-->
